---
title: "PDAC_Rfeatures_Spring2022"
output: html_document
---

## Library and Dataset Import

```{r}
library("dplyr")
library("faux")
library("DataExplorer")
library("caret")
library("randomForest")
library("ggplot2")
library(ggvenn)

TCGAfile = read.csv("/Users/nataliaa.rodriguez/ININ 4998 Pancreatic Cancer/TCGA_Preprocessed.csv")
ICGCfile = read.csv("/Users/nataliaa.rodriguez/ININ 4998 Pancreatic Cancer/ICGC_Preprocessed.csv")
```

## Dataset Information

```{r}
Ix=ICGCfile[,2:35601]
Iy=factor(ICGCfile[,'VS'])

Tx=TCGAfile[,2:20025]
Ty=factor(TCGAfile[,'OS'])
```
TCGA dimensions are `r dim(Tx)`. ICGC dimensions are `r dim(Ix)`. 

## Control Function

```{r}
control <- rfeControl(functions = rfFuncs, # random forest
                      method = "repeatedcv", # repeated cv
                      repeats = 3, # number of repeats
                      number = 5,verbose = FALSE) # number of folds
```

## test: RFE Execution Experimentation with Seed

```{r}
TCGAresult200 <- rfe(x =Tx, y =Ty, sizes = seq(from=1,to=200,by=1), rfeControl = control)
TCGAresult200 

set.seed(1)
TCGAresult200 <- rfe(x =Tx, y =Ty, sizes = seq(from=1,to=200,by=1), rfeControl = control)
TCGAresult200 
```
Results indicated that not assigning a fixed seed would change the random number generator that RFE uses to select the most important variables. A fixed seed will always return the same random numbers from the generator, hence the addition of seed(1).

##TCGA and ICGC RFE with Step=500 up to all variables

```{r}
#Code
set.seed(1) 
TCGAresult_500stp <- rfe(x =Tx, y =Ty, sizes = seq(from=1,to=20025,by=500), rfeControl = control)
TCGAresult_500stp
#Save
TCGAvar_500stp = TCGAfile[,which(names(TCGAfile) %in% predictors(TCGAresult_500stp))]
write.csv(TCGAvar_500stp,file="TCGAvar_500stp.csv",row.names=FALSE)

#Dataframe
TCGAmetric_500stp = as.data.frame(TCGAresult_500stp$results)
TCGAmetric_500stp
#Save
write.csv(TCGAmetric_500stp,file="TCGAmetric_500stp.csv",row.names=FALSE)

#Graph
TCGAgraph_500stp= ggplot(TCGAresult_500stp) + theme_bw()
TCGAgraph_500stp
TCGAerror = TCGAresult_500stp$results$AccuracySD/(sqrt(3*5))
TCGAgraph_500stpEBar = ggplot(TCGAresult_500stp) + theme_bw() + geom_errorbar(aes(x=Variables, ymin=Accuracy-TCGAerror, ymax=Accuracy+TCGAerror),color='purple')
TCGAgraph_500stpEBar
```

```{r}
#Code 
set.seed(1)
ICGCresult_500stp <- rfe(x =Ix, y =Iy, sizes = seq(from=1,to=35601,by=500), rfeControl = control)
ICGCresult_500stp
#Save
ICGCvar_500stp = ICGCfile[,which(names(ICGCfile) %in% predictors(ICGCresult_500stp))]
write.csv(ICGCvar_500stp,file="ICGCvar_500stp.csv",row.names=FALSE)

#Dataframe
ICGCmetric_500stp= as.data.frame(ICGCresult_500stp$results)
ICGCmetric_500stp
#Save
write.csv(ICGCmetric_500stp,file="ICGCmetric_500stp.csv",row.names=FALSE)

#Graph
ICGCgraph_500stp = ggplot(ICGCresult_500stp) + theme_bw()
ICGCgraph_500stp
ICGCerror = TCGAresult_500stp$results$AccuracySD/(sqrt(3*5))
ICGCgraph_500stpEBar = ggplot(ICGCresult_500stp) + theme_bw()+ geom_errorbar(aes(x=Variables, ymin=Accuracy-ICGCerror, ymax=Accuracy+ICGCerror),color='purple')
ICGCgraph_500stpEBar
```

## TCGA and ICGC RFE with Step=1 up to 1000 variables

```{r}
#Code
set.seed(1)
ICGCresult1000_1stp <- rfe(x =Ix, y =Iy, sizes = seq(from=1,to=1000,by=1), rfeControl = control)
ICGCresult1000_1stp
#Save
ICGCvar1000_1stp = ICGCfile[,which(names(ICGCfile) %in% predictors(ICGCresult1000_1stp))]
write.csv(ICGCvar1000_1stp,file="ICGCvar1000_1stp.csv",row.names=FALSE)

#Dataframe
ICGCmetric1000_1stp= as.data.frame(ICGCresult1000_1stp$results)
ICGCmetric1000_1stp
#Save
write.csv(ICGCmetric1000_1stp,file="ICGCmetric1000_1stp.csv",row.names=FALSE)
```

##Additional Runs
```{r}
#Code
set.seed(1)
ICGCresult425 <- rfe(x =Ix, y =Iy, sizes = seq(from=1,to=425,by=1), rfeControl = control)
ICGCresult425
#Save
ICGCvar425 = ICGCfile[,which(names(ICGCfile) %in% predictors(ICGCresult425))]
write.csv(ICGCvar425,file="ICGCvar425.csv",row.names=FALSE)
```

```{r}
#Code
set.seed(1) 
TCGAresult1000_1stp <- rfe(x =Tx, y =Ty, sizes = seq(from=1,to=1000,by=1), rfeControl = control)
TCGAresult1000_1stp
#Save
TCGAvar1000_1stp = TCGAfile[,which(names(TCGAfile) %in% predictors(TCGAresult1000_1stp))]
write.csv(TCGAvar1000_1stp,file="TCGAvar1000_1stp.csv",row.names=FALSE)

#Dataframe
TCGAmetric1000_1stp= as.data.frame(TCGAresult1000_1stp$results)
TCGAmetric1000_1stp
#Save
write.csv(TCGAmetric1000_1stp,file="TCGAmetric1000_1stp.csv",row.names=FALSE)
```

## TCGA and ICGC RFE with Step=5 up to 1000 variables

```{r}
#Code
set.seed(1)
ICGCresult1000_5stp <- rfe(x =Ix, y =Iy, sizes = seq(from=1,to=1000,by=5), rfeControl = control)
ICGCresult1000_5stp
#Save
ICGCvar1000_5stp = ICGCfile[,which(names(ICGCfile) %in% predictors(ICGCresult1000_5stp))]
write.csv(ICGCvar1000_5stp,file="ICGCvar1000_5stp.csv",row.names=FALSE)

#Dataframe
ICGCmetric1000_5stp= as.data.frame(ICGCresult1000_5stp$results)
ICGCmetric1000_5stp
#Save
write.csv(ICGCmetric1000_5stp,file="ICGCmetric1000_5stp.csv",row.names=FALSE)
```

```{r}
set.seed(1) 
TCGAresult1000_5stp <- rfe(x =Tx, y =Ty, sizes = seq(from=1,to=1000,by=5), rfeControl = control)
TCGAresult1000_5stp
#Save
TCGAvar1000_5stp = TCGAfile[,which(names(TCGAfile) %in% predictors(TCGAresult1000_5stp))]
write.csv(TCGAvar1000_5stp,file="TCGAvar1000_5stp.csv",row.names=FALSE)

#Dataframe
TCGAmetric1000_5stp= as.data.frame(TCGAresult1000_5stp$results)
TCGAmetric1000_5stp
#Save
write.csv(TCGAmetric1000_5stp,file="TCGAmetric1000_5stp.csv",row.names=FALSE)
```

## TCGA and ICGC RFE with Step=10 up to 1000 variables

```{r}
set.seed(1)
ICGCresult1000_10stp <- rfe(x =Ix, y =Iy, sizes = seq(from=1,to=1000,by=10), rfeControl = control)
ICGCresult1000_10stp
#Save
ICGCvar1000_10stp = ICGCfile[,which(names(ICGCfile) %in% predictors(ICGCresult1000_10stp))]
write.csv(ICGCvar1000_10stp,file="ICGCvar1000_10stp.csv",row.names=FALSE)

#Dataframe
ICGCmetric1000_10stp= as.data.frame(ICGCresult1000_10stp$results)
ICGCmetric1000_10stp
#Save
write.csv(ICGCmetric1000_10stp,file="ICGCmetric1000_10stp.csv",row.names=FALSE)
```

```{r}
set.seed(1)
#Size = 741
ICGCresult741_10stp <- rfe(x =Ix, y =Iy, rfeControl = control, sizes = 741)
ICGCresult741_10stp
#Save
ICGCvar741_10stp = ICGCfile[,which(names(ICGCfile) %in% ICGCresult741_10stp$optVariables[1:741])] 
write.csv(ICGCvar741_10stp,file="ICGCvar741_10stp.csv",row.names=FALSE)

#Dataframe
ICGCmetric741_10stp= as.data.frame(ICGCresult741_10stp$results)
ICGCmetric741_10stp
#Save
write.csv(ICGCmetric741_10stp,file="ICGCmetric741_10stp.csv",row.names=FALSE)
```

```{r}
set.seed(1) 
TCGAresult1000_10stp <- rfe(x =Tx, y =Ty, sizes = seq(from=1,to=1000,by=10), rfeControl = control)
TCGAresult1000_10stp
#Save
TCGAvar1000_10stp = TCGAfile[,which(names(TCGAfile) %in% predictors(TCGAresult1000_10stp))]
write.csv(TCGAvar1000_10stp,file="TCGAvar1000_10stp.csv",row.names=FALSE)

#Dataframe
TCGAmetric1000_10stp= as.data.frame(TCGAresult1000_10stp$results)
TCGAmetric1000_10stp
#Save
write.csv(TCGAmetric1000_10stp,file="TCGAmetric1000_10stp.csv",row.names=FALSE)
```

## TCGA and ICGC 1000Predictors Venn Diagram

```{r}
#1000 Predictors with Step=1
list1000_1stp = list(TCGA1stp_Features=predictors(TCGAresult1000_1stp),ICGC1stp_Features=predictors(ICGCresult1000_1stp))
VennD1000_1stp= ggvenn(list1000_1stp,show_percentage=FALSE,show_elements = FALSE,fill_color=c("blue","purple"),text_size= 10,set_name_size = 7)
Int1000_1stp = intersect(predictors(TCGAresult1000_1stp),predictors(ICGCresult1000_1stp))
Int1000_1stp_df = as.data.frame(Int1000_1stp)
VennD1000_1stp

#1000 Predictors with Step=5
list1000_5stp = list(TCGA5stp_Features=predictors(TCGAresult1000_5stp),ICGC5stp_Features=predictors(ICGCresult1000_5stp))
VennD1000_5stp= ggvenn(list1000_5stp,show_percentage=FALSE,show_elements = FALSE,fill_color=c("blue","purple"),text_size= 10,set_name_size = 7)
Int1000_5stp = intersect(predictors(TCGAresult1000_5stp),predictors(ICGCresult1000_5stp))
Int1000_5stp_df = as.data.frame(Int1000_5stp)
Int1000_5stp_df
VennD1000_5stp

#1000 Predictors with Step=10
list1000_10stp = list(TCGA10stp_Features=predictors(TCGAresult1000_10stp),ICGC10stp_Features=ICGCresult741_10stp$optVariables[1:741])
VennD1000_10stp= ggvenn(list1000_10stp,show_percentage=FALSE,show_elements = FALSE,fill_color=c("blue","purple"),text_size= 10,set_name_size = 7)
Int1000_10stp = intersect(predictors(TCGAresult1000_10stp),ICGCresult741_10stp$optVariables[1:741])
Int1000_10stp_df = as.data.frame(Int1000_10stp)
Int1000_10stp_df
VennD1000_10stp

#Save as PNG
png("VennD1000_1stp.png")
VennD1000_1stp
dev.off()
png("VennD1000_5stp.png")
VennD1000_5stp
dev.off()
png("VennD1000_10stp.png")
VennD1000_10stp
dev.off()
```

```{r}
#Intersection between Datasets
Int1000_10stp_df
write.csv(Int1000_10stp_df,file="Int1000_10stp.csv",row.names=FALSE)

TCGAint1000_10stp = TCGAfile[,which(names(TCGAfile) %in% Int1000_10stp)]
write.csv(TCGAint1000_10stp,file="TCGAint1000_10stp.csv",row.names=FALSE)

ICGCint741_10stp = ICGCfile[,which(names(ICGCfile) %in% Int1000_10stp) ]
write.csv(ICGCint741_10stp,file="ICGCint741_10stp.csv",row.names=FALSE)
  
Int1000_5stp_df
write.csv(Int1000_5stp_df,file="Int1000_5stp.csv",row.names=FALSE)

TCGAint1000_5stp = TCGAfile[,which(names(TCGAfile) %in% Int1000_5stp)]
write.csv(TCGAint1000_5stp,file="TCGAint1000_5stp.csv",row.names=FALSE)

ICGCint1000_5stp = ICGCfile[,which(names(ICGCfile) %in% Int1000_5stp)]
write.csv(ICGCint1000_5stp,file="ICGCint1000_5stp.csv",row.names=FALSE)

```

```{r}
Int1000_10stp_5stp = intersect(Int1000_10stp,Int1000_5stp)
Int1000_10stp_5stp

list1000_10stp_5stp = list(Int1000_10stp=Int1000_10stp,Int1000_5stp=Int1000_5stp)
VennD1000_10stp_5stp= ggvenn(list1000_10stp_5stp,show_percentage=FALSE,show_elements = FALSE,fill_color=c("blue","purple"),text_size= 10,set_name_size = 7)
VennD1000_10stp_5stp
```








